Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-03 paper/manuscript.tex
Add pct identity to distance_distribution fig
Cleaned up LaTex for PNAS format

@@

\begin{figure*}
\centering
\includegraphics[width=16cm]{figs/distance_distribution/distance_distribution.pdf}
\caption{\label{fig:distance_distribution}
{\bf The HA homologs exhibit many large shifts in preference compared to shifts for other viral protein homologs}
(A) A phylogenetic tree of the HA subtypes, with the two HA's, WSN/1933 H1 and Perth/2009 H3, for which we have measured amino-acid preferences denoted on the tree. 
The WSN/1933 H1 and the Perth/2009 H3 share $\sim$42\% amino-acid identity.
(B) The correlations of the amino-acid preferences for replicates both within and between the two HA homologs. 
The within-Perth/2009 and the within-WSN/1933 correlations are shown in blue and red, respectively.
The between homolog correlations are in gray.
The correlations for replicates within a homolog are higher than for replicates between homologs.
(C) The distribution of shifts in preference for various homolog pairs are shown.
The top two distributions show the distances between each of the HA homologs with the non-homologous HIV Env \comment{cite haddox2017}. 
The center distribution shows the corrected distance between the two HIV Env homologs, which share 86\% amino-acid identity.
The fourth distribution from the top is a null generated by randomizing the HA replicates and computing the distances.
The bottom distribution is the corrected distance between the Perth/2009 H3 and WSN/1933 H1 homologs at all sites that align.
}
\end{figure*}

@@

\subsection*{References}

References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric}. All references should be included in the main manuscript file.

\subsection*{Supporting Information (SI)}

Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.

\subsubsection*{Appendices}

PNAS prefers that authors submit individual source files to ensure readability. If this is not possible, supply a single PDF file that contains all of the SI associated with the paper. This file type will be published in raw format and will not be edited or composed.

@@

% Bibliography
\bibliography{pnas-sample}

>>>>

% added to enable supplementary figures
\usepackage{placeins}
\usepackage{newfloat}
\DeclareFloatingEnvironment[name={Figure}]{suppfigure}
\renewcommand{\thesuppfigure}{S\arabic{suppfigure}}

@@

\begin{figure*}
\centering
\includegraphics[width=17cm]{figs/distance_distribution/distance_distribution.pdf}
\caption{\label{fig:distance_distribution}
{\bf The HA homologs exhibit many large shifts in preference compared to shifts for other viral protein homologs}
(A) A phylogenetic tree of the HA subtypes, with the two HA's, WSN/1933 H1 and Perth/2009 H3, for which we have measured amino-acid preferences denoted on the tree. 
The WSN/1933 H1 and the Perth/2009 H3 share $\sim$42\% amino-acid identity.
(B) The correlations of the amino-acid preferences for replicates both within and between the two HA homologs. 
The within-Perth/2009 and the within-WSN/1933 correlations are shown in blue and red, respectively.
The between homolog correlations are in gray.
The correlations for replicates within a homolog are higher than for replicates between homologs.
(C) The distribution of shifts in preference for various homolog pairs are shown.
The top two distributions show the distances between each of the HA homologs with the non-homologous HIV Env \comment{cite haddox2017}. 
The center distribution shows the corrected distance between the two HIV Env homologs, which share 86\% amino-acid identity.
The fourth distribution from the top is a null generated by randomizing the HA replicates and computing the distances.
The bottom distribution is the corrected distance between the Perth/2009 H3 and WSN/1933 H1 homologs at all sites that align.
}
\end{figure*}

@@

@@

% Bibliography
\subsection*{References}
\bibliography{references}

% Supplementary material temporarily moved until AFTER everything else for initial submission

\onecolumn

\subsection*{Supporting Information (SI)}
\FloatBarrier

\begin{suppfigure}
\centerline{\includegraphics[width=0.5\textwidth]{figs/S01_G78D-T212I/G78D-T212I.pdf}}
\caption{\label{suppfig:Perth2009_mut}
{\bf Characterization of the G78D-T212I Perth/2009 HA variant.} 
(A) 
The G78D-T212I Perth/2009 HA variant grows to higher titers than do viruses carrying the wildtype Perth/2009 HA.
Each virus was generated in duplicate by reverse genetics and passaged once at MOI = 0.01 in MDCK-SIAT1-TMPRSS2 cells.
The rescue and passage viral supernatants were collected at 72 hours post-transfection and 44 hours post-infection, respectively, and titered in MDCK-SIAT1-TMPRSS2 cells. 
The points mark each duplicate and the bar marks the mean.
(B)
The D78 variant remained at a low frequency in natural human H3N2 sequences over the past $~\sim$10 years.
The A212 variant rose to fixation in $~\sim$2011, replacing the T212 variant.
}
\end{suppfigure}
